Genome-wide changes in expression during inflorescence architecture development

### 2015-09-01 ms.Rmd
use phytozome for MADS IDs & peptides
output gene expression truth table from calculateCutoffs

Authors:

Addresses:

@@

Word count

@@

**Discussion: what might these patterns mean biologically?**
**Discussion: which clusters have genes that are already candidates for panicle branching?**

@@

>>>>

Thomas W.R. Harrop^§^[^1], Israr Ud Din^¶^[^1], Veronica Gregis^¶^, Michela Osnato^¶^, Stefan Jouannic^§^, Hélène Adam^§^ and Martin Kater^¶^

[^1]: These authors contributed equally to this work.

| ^§^ Institut de Recherche pour le Développement (IRD), 911 Avenue Agropolis, 34394 Montpellier, France.
| ^¶^ Università degli Studi di Milano, Via Celoria 26, 20133 Milano, Italy.

@@

## Word count

@@

|**Discussion: what might these patterns mean biologically?**
|**Discussion: which clusters have genes that are already candidates for panicle branching?**

@@

### Comparative analysis of MADS family

The primary sequences of *Arabidopsis thaliana*, *Solanum lycopersicum* and *Oryza sativa* MADS proteins were downloaded by querying Phytozome 10.3 [@Goodstein:2012ho] for the PANTHER family PTHR11945 ('MADS BOX PROTEIN') via the `biomaRt` interface (**refs: PANTHER/BIOMART**).
